---
title: "busulfan_manuscript_figure4"
author: "Diana M Abraham"
date: '2022-06-09'
output: html_document
---

```{r}
installed.packages("barcodetrackR")
installed.packages("magrittr")
installed.packages("SummarizedExperiment")
library(dplyr)
library(barcodetrackR)
library (rlang)
require("magrittr")
require("barcodetrackR")
require("SummarizedExperiment")
require(cowplot)
#we adjusted the barcodetrackR package to accomodate for the low clonal contributions from later timepoints in the animal: 11021142 - so we read in a customized barcode ggheatmap function for that animal's analysis 
```



#read in the counts files for the animals in Figure 4
```{r}
#the second & third refer to the 3 busulfan animals
#second = M10U004
#third = H84D
df_counts_first<-read.delim(("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/final_counts_files/M11021142_combined_20220510_lib15counts.txt"), row.names = 1)
df_counts_second<-read.delim(("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/final_counts_files/M10U004_combined_20220509_counts.txt"), row.names = 1)
df_counts_third<-read.delim(("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/final_counts_files/H84D_combined_20220510_counts.txt"), row.names = 1)

#for the figure 4 we use two TBI animals to compare - ZJ31 and ZG66
df_counts_ZJ31<-read.delim(("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/final_counts_files/ZJ31_combined_20210302_counts.txt"), row.names = 1)
df_counts_ZG66<-df_counts_ZG66<-read.delim(("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/final_counts_files/ZG66_combined_20220207_counts_cleaned.txt"), row.names = 1)
```

#read in the metadata files for the animals in Figure 4
```{r}
#Busulfan
metadata_df_first<-read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/final_metadata_files/M11021142_20220510_NElib_metadata.txt")
metadata_df_second<-read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/final_metadata_files/10U004_20220510_NELib_metadata.txt")
metadata_df_third<-read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/final_metadata_files/H84D_20220510_NElib_metadata.txt")

#TBI
metadata_ZJ31<-read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/final_metadata_files/ZJ31_20210302_metadata_edited.txt") 
metadata_ZG66<-read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/final_metadata_files/ZG66_20220207_metadata_edited.txt")
```

#create SEs for each animal
#we use a threshold of 0 since when the metadata and count files are being generated we take out any 0 values
```{r}
first_SE <- create_SE(your_data = df_counts_first,
                      meta_data = metadata_df_first,
                      threshold = 0)
second_SE <- create_SE(your_data = df_counts_second,
                       meta_data = metadata_df_second,
                       threshold = 0)
third_SE <- create_SE(your_data = df_counts_third,
                      meta_data = metadata_df_third,
                      threshold = 0)
ZJ31_SE <- create_SE(your_data = df_counts_ZJ31,
                     meta_data = metadata_ZJ31,
                     threshold = 0)
ZG66_SE<-create_SE(your_data = df_counts_ZG66,
                   meta_data = metadata_ZG66,
                   threshold = 0) 
```


#load the samplelist for the first monkey- M11021142
```{r}
df_counts_first<- df_counts_first[,metadata_df_first$SAMPLENAME]

# Make sure everything is numeric
df_counts_first<- data.frame(apply(df_counts_first, 2,            
                                   function(x) as.numeric(as.character(x))),
                             row.names = rownames(df_counts_first))

sample_list_first_NK_PB <- read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/samplelist/NK_PB/M11021142_NK_PB_samplelist.txt",sep = "\t", header=F)

colnames(sample_list_first_NK_PB) <- "SAMPLENAME"
sample_list_first_NK_PB<-sample_list_first_NK_PB$SAMPLENAME

# find the indices corresponding to each sample in the metadata & countdata  
sample_index_first_NK_PB <- rep(NA, length(sample_list_first_NK_PB))
for (i in 1:length(sample_list_first_NK_PB)){
  sample_index_first_NK_PB[i] <- which(metadata_df_first$SAMPLENAME == sample_list_first_NK_PB[i])
}
```

#load the samplelist for the second monkey- M10U004
```{r}
df_counts_second<- df_counts_second[,metadata_df_second$SAMPLENAME]

# Make sure everything is numeric
df_counts_second<- data.frame(apply(df_counts_second, 2,            
                                    function(x) as.numeric(as.character(x))),
                              row.names = rownames(df_counts_second))

sample_list_second_NK_PB <- read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/samplelist/NK_PB/M10U004_NK_PB_samplelist.txt",sep = "\t", header=F)

colnames(sample_list_second_NK_PB) <- "SAMPLENAME"
sample_list_second_NK_PB<-sample_list_second_NK_PB$SAMPLENAME

# find the indices corresponding to each sample in the metadata & countdata  
sample_index_second_NK_PB <- rep(NA, length(sample_list_second_NK_PB))
for (i in 1:length(sample_list_second_NK_PB)){
  sample_index_second_NK_PB[i] <- which(metadata_df_second$SAMPLENAME == sample_list_second_NK_PB[i])
}
```
#load the samplelist for the third monkey- H84D
```{r}
df_counts_third<- df_counts_third[,metadata_df_third$SAMPLENAME]

# Make sure everything is numeric
df_counts_third<- data.frame(apply(df_counts_third, 2,            
                                   function(x) as.numeric(as.character(x))),
                             row.names = rownames(df_counts_third))

sample_list_third_NK_PB <- read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/samplelist/NK_PB/H84D_NK_PB_samplelist.txt",sep = "\t", header=F)

colnames(sample_list_third_NK_PB) <- "SAMPLENAME"
sample_list_third_NK_PB<-sample_list_third_NK_PB$SAMPLENAME

# find the indices corresponding to each sample in the metadata & countdata  
sample_index_third_NK_PB <- rep(NA, length(sample_list_third_NK_PB))
for (i in 1:length(sample_list_third_NK_PB)){
  sample_index_third_NK_PB[i] <- which(metadata_df_third$SAMPLENAME == sample_list_third_NK_PB[i])
}
```
#ZG66 samplelist for NK_PB Heatmap
```{r}
df_counts_ZG66<- df_counts_ZG66[,metadata_ZG66$SAMPLENAME]

# Make sure everything is numeric
df_counts_ZG66<- data.frame(apply(df_counts_ZG66, 2,            
                                  function(x) as.numeric(as.character(x))),
                            row.names = rownames(df_counts_ZG66))

sample_list_ZG66_NK_PB <- read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/samplelist/NK_PB/ZG66_NK_PB_samplelist.txt",sep = "\t", header=F)

colnames(sample_list_ZG66_NK_PB) <- "SAMPLENAME"
sample_list_ZG66_NK_PB<-sample_list_ZG66_NK_PB$SAMPLENAME

# find the indices corresponding to each sample in the metadata & countdata  
sample_index_ZG66_NK_PB <- rep(NA, length(sample_list_ZG66_NK_PB))
for (i in 1:length(sample_list_ZG66_NK_PB)){
  sample_index_ZG66_NK_PB[i] <- which(metadata_ZG66$SAMPLENAME == sample_list_ZG66_NK_PB[i])
}
```
#ZJ31 samplelist for NK_PB Heatmap
```{r}
df_counts_ZJ31<- df_counts_ZJ31[,metadata_ZJ31$SAMPLENAME]

# Make sure everything is numeric
df_counts_ZJ31<- data.frame(apply(df_counts_ZJ31, 2,            
                                  function(x) as.numeric(as.character(x))),
                            row.names = rownames(df_counts_ZJ31))

sample_list_ZJ31_NK_PB <- read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/samplelist/NK_PB/ZJ31_NK_PB_samplelist.txt",sep = "\t", header=F)

colnames(sample_list_ZJ31_NK_PB) <- "SAMPLENAME"
sample_list_ZJ31_NK_PB<-sample_list_ZJ31_NK_PB$SAMPLENAME

# find the indices corresponding to each sample in the metadata & countdata  
sample_index_ZJ31_NK_PB <- rep(NA, length(sample_list_ZJ31_NK_PB))
for (i in 1:length(sample_list_ZJ31_NK_PB)){
  sample_index_ZJ31_NK_PB[i] <- which(metadata_ZJ31$SAMPLENAME == sample_list_ZJ31_NK_PB[i])
}
```


```{r}
first_NK_PB_sample_selection<- colData(first_SE)$SAMPLENAME[sample_index_first_NK_PB]

second_NK_PB_sample_selection<- colData(second_SE)$SAMPLENAME[sample_index_second_NK_PB]
#don't include 1m for H84D
third_NK_PB_sample_selection<- colData(third_SE)$SAMPLENAME[sample_index_third_NK_PB]

ZJ31_NK_PB_sample_selection <- colData(ZJ31_SE)$SAMPLENAME[sample_index_ZJ31_NK_PB]
ZG66_NK_PB_sample_selection <- colData(ZG66_SE)$SAMPLENAME[sample_index_ZG66_NK_PB]
```

```{r}
first_NK_PB_samplenames<- paste(paste(metadata_df_first[sample_index_first_NK_PB, ]$Month_timepoint, "m", sep = "_"),
                             metadata_df_first[sample_index_first_NK_PB, ]$Other, metadata_df_first[sample_index_first_NK_PB, ]$Cell.Type)

second_NK_PB_samplenames<-paste(paste(metadata_df_second[sample_index_second_NK_PB, ]$Month_timepoint, "m", sep = "_"), 
                             paste(metadata_df_second[sample_index_second_NK_PB, ]$Experiment, metadata_df_second[sample_index_second_NK_PB, ]$Other, sep="_"), metadata_df_second[sample_index_second_NK_PB, ]$Cell.Type)

third_NK_PB_samplenames<-paste(paste(metadata_df_third[sample_index_third_NK_PB, ]$Month_timepoint, "m", sep = "_"), 
                            paste(metadata_df_third[sample_index_third_NK_PB, ]$Experiment, metadata_df_third[sample_index_third_NK_PB, ]$Other, sep="_"), 
                            metadata_df_third[sample_index_third_NK_PB, ]$Cell.Type)
#treat 3m GR as 4m Gr

ZG66_NK_PB_samplenames<-paste(paste(metadata_ZG66[sample_index_ZG66_NK_PB, ]$Month_timepoint, "m", sep = "_"), 
                            metadata_ZG66[sample_index_ZG66_NK_PB, ]$Other, 
                            metadata_ZG66[sample_index_ZG66_NK_PB, ]$simple_cell_type)

ZJ31_NK_PB_samplenames<-paste( paste(metadata_ZJ31[sample_index_ZJ31_NK_PB, ]$months, "m", sep = "_"), 
                             metadata_ZJ31[sample_index_ZJ31_NK_PB, ]$source, 
                             metadata_ZJ31[sample_index_ZJ31_NK_PB, ]$simple_cell_type)

```

#NK PB Heatmap 
```{r}
first_NK_heatmap<-barcode_ggheatmap(first_SE[,first_NK_PB_sample_selection],
                                    plot_labels = first_NK_PB_samplenames,
                                    n_clones = 10, label_size = 7, your_title = "11021142 PB NK Heatmap")

second_NK_heatmap<-barcode_ggheatmap(second_SE[,second_NK_PB_sample_selection], 
                                         plot_labels = second_NK_PB_samplenames,
                                     n_clones = 10, label_size = 7, your_title = "10U004 PB NK Heatmap")
third_NK_heatmap<-barcode_ggheatmap(third_SE[,third_NK_PB_sample_selection],
                                                    plot_labels = third_NK_PB_samplenames,
                                    n_clones = 10, label_size = 7, your_title = "H84D PB NK Heatmap")

ZJ31_NK_heatmap<-barcode_ggheatmap(ZJ31_SE[,ZJ31_NK_PB_sample_selection],
                                   plot_labels = ZJ31_NK_PB_samplenames, 
                                       n_clones = 10, label_size = 7, your_title = "ZJ31 PB NK Heatmap")
ZG66_NK_heatmap<-barcode_ggheatmap(ZG66_SE[,ZG66_NK_PB_sample_selection], 
                                   plot_labels = ZG66_NK_PB_samplenames, 
                                       n_clones = 10, label_size = 7, your_title = "ZG66 PB NK Heatmap")
```

```{r}
first_NK_heatmap
second_NK_heatmap
third_NK_heatmap
ZJ31_NK_heatmap
ZG66_NK_heatmap
```

#NK PB Pearson Correlation Plots
```{r}
first_NK_corplot<-cor_plot(first_SE[,first_NK_PB_sample_selection], plot_labels = first_NK_PB_samplenames, no_negatives = T, your_title = "11021142 PB NK Pearson Correlation Plot")

second_NK_corplot<-cor_plot(second_SE[,second_NK_PB_sample_selection], plot_labels = second_NK_PB_samplenames, no_negatives = T, your_title = "10U004 PB NK Pearson Correlation Plot")
third_NK_corplot<-cor_plot(third_SE[,third_NK_PB_sample_selection], label_size = 10, plot_labels = third_NK_PB_samplenames, no_negatives = T, your_title = "H84D PB NK Pearson Correlation Plot")
ZJ31_NK_corplot<-cor_plot(ZJ31_SE[,ZJ31_NK_PB_sample_selection], plot_labels = ZJ31_NK_PB_samplenames, no_negatives = T, your_title = "ZJ31 PB NK Pearson Correlation Plot")
ZG66_NK_corplot<-cor_plot(ZG66_SE[,ZG66_NK_PB_sample_selection], plot_labels = ZG66_NK_PB_samplenames, no_negatives = T, your_title = "ZG66 PB NK Pearson Correlation Plot")
```

```{r}
first_NK_corplot
second_NK_corplot
third_NK_corplot
ZJ31_NK_corplot
ZG66_NK_corplot
```

#NK Ridge Plots
##Granulocyte (Gr) vs CD16+ NK 
```{r}
first_gr_vs_cd16p<-bias_ridge_plot(first_SE[,first_NK_PB_sample_selection], 
                               split_bias_on = "Cell.Type", 
                               bias_1 = "Gr", 
                               bias_2 = "CD16+",
                               split_bias_over = "Month_timepoint",
                               bias_over = c("1", "3","4.5","9", "13"),
                               remove_unique = FALSE,
                               weighted = TRUE,
                               text_size = 16,
                               add_dots = TRUE,
                               return_table = FALSE)

second_gr_vs_cd16p<-bias_ridge_plot(second_SE[,second_NK_PB_sample_selection], 
                               split_bias_on = "Cell.Type", 
                               bias_1 = "Gr", 
                               bias_2 = "CD16+",
                               split_bias_over = "Month_timepoint",
                               bias_over = c("1.5", "2", "3", "9", "16", "20", "22.5"),
                               remove_unique = FALSE,
                               weighted = TRUE,
                               text_size = 16,
                               add_dots = TRUE,
                               return_table = FALSE)

third_gr_vs_cd16p<-bias_ridge_plot(third_SE[,third_NK_PB_sample_selection], 
                               split_bias_on = "Cell.Type", 
                               bias_1 = "Gr", 
                               bias_2 = "CD16+",
                               split_bias_over = "Month_timepoint",
                               bias_over = c("2", "3","6","9", "12","14.5", "18"),
                               weighted = T,
                               add_dots = T,
                               text_size = 16,
                               remove_unique = FALSE)

ZG66_gr_vs_cd16p<-bias_ridge_plot(ZG66_SE[,ZG66_NK_PB_sample_selection], 
                                                 split_bias_on = "simple_cell_type", 
                                                 bias_1 = "Gr", 
                                                 bias_2 = "CD16+",
                                                 split_bias_over = "Month_timepoint",
                                                 bias_over = c("4.5", "6.5", "12","17", "27", "36"),
                                                 remove_unique = FALSE,
                                                 weighted = TRUE,
                                                 text_size = 16,
                                                 add_dots = TRUE,
                                                 return_table = FALSE)

ZJ31_gr_vs_cd16p<-bias_ridge_plot(ZJ31_SE[,ZJ31_NK_PB_sample_selection], 
                                            split_bias_on = "simple_cell_type", 
                                            bias_1 = "Gr", 
                                            bias_2 = "CD16+",
                                            split_bias_over = "months",
                                            bias_over = c("6", "9.5","12","20", "33"),
                                            remove_unique = FALSE,
                                            weighted = TRUE,
                                            text_size = 16,
                                            add_dots = TRUE,
                                            return_table = FALSE)
```

```{r}
first_gr_vs_cd16p
second_gr_vs_cd16p
third_gr_vs_cd16p
ZG66_gr_vs_cd16p
ZJ31_gr_vs_cd16p
```
