---
title: "busulfan_manuscript_figure3_markdown"
author: "Diana M Abraham"
date: '2022-06-09'
output: html_document
---

```{r}
installed.packages("barcodetrackR")
installed.packages("magrittr")
installed.packages("SummarizedExperiment")
library(dplyr)
library(barcodetrackR)
library (rlang)
require("magrittr")
require("barcodetrackR")
require("SummarizedExperiment")
require(cowplot)
#we adjusted the barcodetrackR package to accomodate for the low clonal contributions from later timepoints in the animal: 11021142 - so we read in a customized barcode ggheatmap function for that animal's analysis 
barcode_ggheatmap_first<-source("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/customized_functions/barcode_ggheatmap_42.R")
barcode_ggheatmap_first<-barcode_ggheatmap_first$value
```

#read in the counts files for the animals in Figure 3
```{r}
#the first, second, third refer to the 3 busulfan animals
#first = M11021142
#second = M10U004
#third = H84D
df_counts_first<-read.delim(("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/final_counts_files/M11021142_combined_20220510_lib15counts.txt"), row.names = 1)
df_counts_second<-read.delim(("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/final_counts_files/M10U004_combined_20220509_counts.txt"), row.names = 1)
df_counts_third<-read.delim(("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/final_counts_files/H84D_combined_20220510_counts.txt"), row.names = 1)

#for the figure 3 we use one TBI animal to compare - ZJ31
df_counts_ZJ31<-read.delim(("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/final_counts_files/ZJ31_combined_20210302_counts.txt"), row.names = 1)
```

#read in the metadata files for the animals in Figure 3
```{r}
metadata_df_first<-read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/final_metadata_files/M11021142_20220510_NElib_metadata.txt")
metadata_df_second<-read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/final_metadata_files/10U004_20220510_NELib_metadata.txt")
metadata_df_third<-read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/final_metadata_files/H84D_20220510_NElib_metadata.txt")
metadata_ZJ31<-read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/final_metadata_files/ZJ31_20210302_metadata_edited.txt") 

```

#load the samplelist for the first monkey- M11021142
```{r}
df_counts_first<- df_counts_first[,metadata_df_first$SAMPLENAME]

# Make sure everything is numeric
df_counts_first<- data.frame(apply(df_counts_first, 2,            
                               function(x) as.numeric(as.character(x))),
                         row.names = rownames(df_counts_first))

sample_list_first_BM <- read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/samplelist/BM/M11021142_BM_samplelist.txt",sep = "\t", header=F)

colnames(sample_list_first_BM) <- "SAMPLENAME"
sample_list_first_BM<-sample_list_first_BM$SAMPLENAME

# find the indices corresponding to each sample in the metadata & countdata  
sample_index_first_BM <- rep(NA, length(sample_list_first_BM))
for (i in 1:length(sample_list_first_BM)){
  sample_index_first_BM[i] <- which(metadata_df_first$SAMPLENAME == sample_list_first_BM[i])
}
```

#load the samplelist for the second monkey- M10U004
```{r}
df_counts_second<- df_counts_second[,metadata_df_second$SAMPLENAME]

# Make sure everything is numeric
df_counts_second<- data.frame(apply(df_counts_second, 2,            
                               function(x) as.numeric(as.character(x))),
                         row.names = rownames(df_counts_second))

sample_list_second_BM <- read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/samplelist/BM/M10U004_BM_samplelist.txt",sep = "\t", header=F)

colnames(sample_list_second_BM) <- "SAMPLENAME"
sample_list_second_BM<-sample_list_second_BM$SAMPLENAME

# find the indices corresponding to each sample in the metadata & countdata  
sample_index_second_BM <- rep(NA, length(sample_list_second_BM))
for (i in 1:length(sample_list_second_BM)){
  sample_index_second_BM[i] <- which(metadata_df_second$SAMPLENAME == sample_list_second_BM[i])
}
```
#load the samplelist for the third monkey- H84D
```{r}
df_counts_third<- df_counts_third[,metadata_df_third$SAMPLENAME]

# Make sure everything is numeric
df_counts_third<- data.frame(apply(df_counts_third, 2,            
                                    function(x) as.numeric(as.character(x))),
                              row.names = rownames(df_counts_third))

sample_list_third_BM <- read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/samplelist/BM/H84D_BM_samplelist.txt",sep = "\t", header=F)

colnames(sample_list_third_BM) <- "SAMPLENAME"
sample_list_third_BM<-sample_list_third_BM$SAMPLENAME

# find the indices corresponding to each sample in the metadata & countdata  
sample_index_third_BM <- rep(NA, length(sample_list_third_BM))
for (i in 1:length(sample_list_third_BM)){
  sample_index_third_BM[i] <- which(metadata_df_third$SAMPLENAME == sample_list_third_BM[i])
}
```

#ZJ31
```{r}
df_counts_ZJ31<- df_counts_ZJ31[,metadata_ZJ31$SAMPLENAME]

# Make sure everything is numeric
df_counts_ZJ31<- data.frame(apply(df_counts_ZJ31, 2,            
                                   function(x) as.numeric(as.character(x))),
                             row.names = rownames(df_counts_ZJ31))

sample_list_ZJ31_BM <- read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/samplelist/BM/ZJ31_BM_samplelist.txt",sep = "\t", header=F)

colnames(sample_list_ZJ31_BM) <- "SAMPLENAME"
sample_list_ZJ31_BM<-sample_list_ZJ31_BM$SAMPLENAME

# find the indices corresponding to each sample in the metadata & countdata  
sample_index_ZJ31_BM <- rep(NA, length(sample_list_ZJ31_BM))
for (i in 1:length(sample_list_ZJ31_BM)){
  sample_index_ZJ31_BM[i] <- which(metadata_ZJ31$SAMPLENAME == sample_list_ZJ31_BM[i])
}
```


#create SEs for each animal

#we use a threshold of 0 since when the metadata and count files are being generated we take out any 0 values
```{r}
first_SE <- create_SE(your_data = df_counts_first,
                      meta_data = metadata_df_first,
                      threshold = 0)
second_SE <- create_SE(your_data = df_counts_second,
                       meta_data = metadata_df_second,
                       threshold = 0)
third_SE <- create_SE(your_data = df_counts_third,
                      meta_data = metadata_df_third,
                      threshold = 0)
ZJ31_SE <- create_SE(your_data = df_counts_ZJ31,
                     meta_data = metadata_ZJ31,
                     threshold = 0)
```

```{r}
#only included these two timepoints because low clonal abundance/contribution at later timepoints post 18.5m 

first_BM_sample_selection<- colData(first_SE)$SAMPLENAME[sample_index_first_BM]

second_BM_sample_selection<- colData(second_SE)$SAMPLENAME[sample_index_second_BM]

third_BM_sample_selection <- colData(third_SE)$SAMPLENAME[sample_index_third_BM]

ZJ31_BM_sample_selection <- colData(ZJ31_SE)$SAMPLENAME[sample_index_ZJ31_BM]
```

#read in BM samplenames

```{r}
first_BM_samplenames<- paste( paste(metadata_df_first[sample_index_first_BM, ]$Month_timepoint, "m", sep = "_"), metadata_df_first[sample_index_first_BM, ]$Other, metadata_df_first[sample_index_first_BM, ]$Cell.Type)

second_BM_samplenames<-paste( paste(metadata_df_second[sample_index_second_BM, ]$Month_timepoint, "m", sep = "_"), paste(metadata_df_second[sample_index_second_BM, ]$Experiment, metadata_df_second[sample_index_second_BM, ]$Other, sep="_"), metadata_df_second[sample_index_second_BM, ]$Cell.Type)

third_BM_sample_names<-paste( paste(metadata_df_third[sample_index_third_BM, ]$Month_timepoint, "m", sep = "_"), paste(metadata_df_third[sample_index_third_BM, ]$Experiment, metadata_df_third[sample_index_third_BM, ]$Other, sep="_"), metadata_df_third[sample_index_third_BM, ]$Cell.Type)
#treat 3m GR as 4m Gr

ZJ31_BM_sample_names<-paste( paste(metadata_ZJ31[sample_index_ZJ31_BM, ]$months, "m", sep = "_"), metadata_ZJ31[sample_index_ZJ31_BM, ]$source, metadata_ZJ31[sample_index_ZJ31_BM, ]$simple_cell_type)
```

#generate BM heatmaps
```{r}
first_BM_heatmap<-barcode_ggheatmap_first(first_SE[,first_BM_sample_selection], 
                                          plot_labels= first_BM_samplenames,  
                                          n_clones = 10, label_size = 10,  cellnote_size = 3, your_title = "11021142 BM Heatmap")

second_BM_heatmap<-barcode_ggheatmap(second_SE[,second_BM_sample_selection], 
                                     plot_labels = second_BM_samplenames,
                                     n_clones = 10, label_size = 10,  cellnote_size = 3,  your_title = "10U004 BM Heatmap")

third_BM_heatmap<-barcode_ggheatmap(third_SE[,third_BM_sample_selection],
                                    plot_labels = third_BM_sample_names, 
                                    n_clones = 10, label_size = 10, cellnote_size = 3,  your_title = "H84D BM Heatmap")

ZJ31_BM_heatmap<-barcode_ggheatmap(ZJ31_SE[,ZJ31_BM_sample_selection], 
                                  plot_labels = ZJ31_BM_sample_names,
                                     n_clones = 10, label_size = 10,  cellnote_size = 3,  your_title = "ZJ31 BM Heatmap")
```

#read out the BM heatmaps
```{r}
first_BM_heatmap
second_BM_heatmap
third_BM_heatmap
ZJ31_BM_heatmap
```

#generate BM pearson correlation plots

```{r}
first_BM_corplot<-cor_plot(first_SE[,first_BM_sample_selection], plot_labels = first_BM_samplenames, 
                           no_negatives = T, label_size = 12, your_title = "11021142 BM Pearson Correlation Plot")
second_BM_corplot<-cor_plot(second_SE[,second_BM_sample_selection], plot_labels = second_BM_samplenames, 
                            no_negatives = T, label_size = 12, your_title = "10U004 BM Pearson Correlation Plot")
third_BM_corplot<-cor_plot(third_SE[,third_BM_sample_selection], label_size = 12, 
                           plot_labels = third_BM_sample_names, no_negatives = T, your_title = "H84D BM Pearson Correlation Plot")
ZJ31_BM_corplot<-cor_plot(ZJ31_SE[,ZJ31_BM_sample_selection],plot_labels = ZJ31_BM_sample_names,
                          no_negatives = T, label_size = 12, your_title = "ZJ31 BM Pearson Correlation Plot")

```

#read out the BM pearson correlation plots
```{r}
first_BM_corplot
second_BM_corplot
third_BM_corplot
ZJ31_BM_corplot
```

