---
title: "Busulfan Manuscript Figure 2"
author: "Diana M Abraham"
date: '2022-06-09'
output: html_document
---

##################SETTING UP###################
#if first time using barcodetrackR
```{r}
install.packages("barcodetrackR")
install.packages("magrittr")
install.packages("SummarizedExperiment")
```

#load up the necessary packages and libraries and functions
```{r}
installed.packages("barcodetrackR")
installed.packages("magrittr")
installed.packages("SummarizedExperiment")
library(dplyr)
library(barcodetrackR)
library (rlang)
library(ggplot2)
library(RColorBrewer)
require("magrittr")
require("barcodetrackR")
require("SummarizedExperiment")
#we adjusted the barcodetrackR package and so here is the customized function that we used to calculate the cumulative counts
clonal_count_v3<-source("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/customized_functions/clonal_counts_v3.R") 
clonal_count_v3<-clonal_count_v3$value

#we adjusted the barcodetrackR package to accomodate for the low clonal contributions from later timepoints in the animal: 11021142 - so we read in a customized barcode ggheatmap function for that animal's analysis 
barcode_ggheatmap_first<-source("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/customized_functions/barcode_ggheatmap_42.R")
barcode_ggheatmap_first<-barcode_ggheatmap_first$value
autocorrelation.plot<-source("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/customized_functions/autocorrelation_plot.R")
autocorrelation.plot<-autocorrelation.plot$value
```

#read in the counts files for the animals in Figure 2
```{r}
#the first, second, third refer to the 3 busulfan animals
#first = M11021142
#second = M10U004
#third = H84D
df_counts_first<-read.delim(("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/final_counts_files/M11021142_combined_20220510_lib15counts.txt"), row.names = 1)
df_counts_second<-read.delim(("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/final_counts_files/M10U004_combined_20220509_counts.txt"), row.names = 1)
df_counts_third<-read.delim(("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/final_counts_files/H84D_combined_20220510_counts.txt"), row.names = 1)

#for the figure 2 we use one TBI animal to compare - ZG66
df_counts_ZG66<-df_counts_ZG66<-read.delim(("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/final_counts_files/ZG66_combined_20220207_counts_cleaned.txt"), row.names = 1)

#as a back-up we use ZJ31 as the other TBI animal to compare clonal counts
df_counts_ZJ31<-read.delim(("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/final_counts_files/ZJ31_combined_20210302_counts.txt"), row.names = 1)

df_counts_ZK22<-read.delim(("/Volumes/dirgroup/TSCBB/LAB/Barcoded Monkeys/ZK22/Processed Data/20210611/ZK22_combined_20210611_counts.txt"), row.names = 1)

df_counts_ZH33<-read.delim(("/Volumes/dirgroup/TSCBB/LAB/Barcoded Monkeys/ZH33/Processed Data/20191107/ZH33_combined_20191107_counts.txt"), row.names = 1)

df_counts_ZH19<-read.delim(("/Volumes/dirgroup/TSCBB/LAB/Barcoded Monkeys/ZH19/Processed Data/20191101/ZH19_combined_20191101_cleaned_counts.txt"), row.names = 1)
```

#read in the metadata files for the animals in Figure 2
```{r}
metadata_df_first<-read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/final_metadata_files/M11021142_20220510_NElib_metadata.txt")
metadata_df_second<-read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/final_metadata_files/10U004_20220510_NELib_metadata.txt")
metadata_df_third<-read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/final_metadata_files/H84D_20220510_NElib_metadata.txt")
metadata_ZG66<-read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/final_metadata_files/ZG66_20220207_metadata_edited.txt")
metadata_ZJ31<-read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/final_metadata_files/ZJ31_20210302_metadata_edited.txt") 
metadata_ZK22<-read.delim("/Volumes/dirgroup/TSCBB/LAB/Barcoded Monkeys/ZK22/Processed Data/20210611/ZK22_metadata_20220611_edited_20220707.txt")
metadata_ZH33<-read.delim("/Volumes/dirgroup/TSCBB/LAB/Barcoded Monkeys/ZH33/Processed Data/20191107/ZH33_combined_20191107_metadata_20220707.txt") 
metadata_ZH19<-read.delim("/Volumes/dirgroup/TSCBB/LAB/Barcoded Monkeys/ZH19/Processed Data/20191101/ZH19_combined_20191101_cleaned_metadata_edited_20220706.txt") #Month_timepoint
```
#create SEs for each animal
#we use a threshold of 0 since when the metadata and count files are being generated we take out any 0 values
```{r}
first_SE <- create_SE(your_data = df_counts_first,
                      meta_data = metadata_df_first,
                      threshold = 0)
second_SE <- create_SE(your_data = df_counts_second,
                       meta_data = metadata_df_second,
                       threshold = 0)
third_SE <- create_SE(your_data = df_counts_third,
                      meta_data = metadata_df_third,
                      threshold = 0)
ZG66_SE<-create_SE(your_data = df_counts_ZG66,
                   meta_data = metadata_ZG66,
                   threshold = 0) 

#for clonal counts we applied thresholding to be consistent with previous publications that utilize these TBI animals
ZG66_SE_clonal_counts<-create_SE(your_data = df_counts_ZG66,
                   meta_data = metadata_ZG66,
                   threshold = 0.0005) 
ZK22_SE<-create_SE(your_data = df_counts_ZK22,
                   meta_data = metadata_ZK22,
                   threshold =  0.0005)
ZJ31_SE <- create_SE(your_data = df_counts_ZJ31,
                     meta_data = metadata_ZJ31,
                     threshold =  0.0005)

ZH33_SE<-create_SE(your_data = df_counts_ZH33,
                   meta_data = metadata_ZH33,
                   threshold =  0.0005)

ZG66_SE<-create_SE(your_data = df_counts_ZG66,
                   meta_data = metadata_ZG66,
                   threshold =  0.0005)
ZH19_SE<-create_SE(your_data = df_counts_ZH19,
                   meta_data = metadata_ZH19,
                   threshold =  0.0005)

ZK22_SE_shannon<-create_SE(your_data = df_counts_ZK22,
                   meta_data = metadata_ZK22,
                   threshold =  0)
ZJ31_SE_shannon <- create_SE(your_data = df_counts_ZJ31,
                     meta_data = metadata_ZJ31,
                     threshold =  0)

ZH33_SE_shannon<-create_SE(your_data = df_counts_ZH33,
                   meta_data = metadata_ZH33,
                   threshold =  0)
ZH19_SE_shannon<-create_SE(your_data = df_counts_ZH19,
                   meta_data = metadata_ZH19,
                   threshold =  0)
#thresholding 0.05% of the 4 million reads to get rid of 2000 reads that aren't helpful for data analysis, this is consistent with previous publications for ZG66 for clonal counts only
```

#load the samplelist for the first monkey- M11021142
```{r}
df_counts_first<- df_counts_first[,metadata_df_first$SAMPLENAME]

# Make sure everything is numeric
df_counts_first<- data.frame(apply(df_counts_first, 2,            
                               function(x) as.numeric(as.character(x))),
                         row.names = rownames(df_counts_first))

sample_list_first_PB <- read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/samplelist/PB/M11021142_PB_samplelist.txt",sep = "\t", header=F)

colnames(sample_list_first_PB) <- "SAMPLENAME"
sample_list_first_PB<-sample_list_first_PB$SAMPLENAME

# find the indices corresponding to each sample in the metadata & countdata  
sample_index_first_PB <- rep(NA, length(sample_list_first_PB))
for (i in 1:length(sample_list_first_PB)){
  sample_index_first_PB[i] <- which(metadata_df_first$SAMPLENAME == sample_list_first_PB[i])
}
```

#load the samplelist for the second monkey- M10U004
```{r}
df_counts_second<- df_counts_second[,metadata_df_second$SAMPLENAME]

# Make sure everything is numeric
df_counts_second<- data.frame(apply(df_counts_second, 2,            
                               function(x) as.numeric(as.character(x))),
                         row.names = rownames(df_counts_second))

sample_list_second_PB <- read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/samplelist/PB/M10U004_PB_samplelist.txt",sep = "\t", header=F)

colnames(sample_list_second_PB) <- "SAMPLENAME"
sample_list_second_PB<-sample_list_second_PB$SAMPLENAME

# find the indices corresponding to each sample in the metadata & countdata  
sample_index_second_PB <- rep(NA, length(sample_list_second_PB))
for (i in 1:length(sample_list_second_PB)){
  sample_index_second_PB[i] <- which(metadata_df_second$SAMPLENAME == sample_list_second_PB[i])
}
```
#load the samplelist for the third monkey- H84D
```{r}
df_counts_third<- df_counts_third[,metadata_df_third$SAMPLENAME]

# Make sure everything is numeric
df_counts_third<- data.frame(apply(df_counts_third, 2,            
                                    function(x) as.numeric(as.character(x))),
                              row.names = rownames(df_counts_third))

sample_list_third_PB <- read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/samplelist/PB/H84D_PB_samplelist.txt",sep = "\t", header=F)

colnames(sample_list_third_PB) <- "SAMPLENAME"
sample_list_third_PB<-sample_list_third_PB$SAMPLENAME

# find the indices corresponding to each sample in the metadata & countdata  
sample_index_third_PB <- rep(NA, length(sample_list_third_PB))
for (i in 1:length(sample_list_third_PB)){
  sample_index_third_PB[i] <- which(metadata_df_third$SAMPLENAME == sample_list_third_PB[i])
}
```
#ZG66 samplelist for PB Heatmap
```{r}
df_counts_ZG66<- df_counts_ZG66[,metadata_ZG66$SAMPLENAME]

# Make sure everything is numeric
df_counts_ZG66<- data.frame(apply(df_counts_ZG66, 2,            
                                    function(x) as.numeric(as.character(x))),
                              row.names = rownames(df_counts_ZG66))

sample_list_ZG66_PB <- read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/samplelist/PB/ZG66_PB_samplelist.txt",sep = "\t", header=F)

colnames(sample_list_ZG66_PB) <- "SAMPLENAME"
sample_list_ZG66_PB<-sample_list_ZG66_PB$SAMPLENAME

# find the indices corresponding to each sample in the metadata & countdata  
sample_index_ZG66_PB <- rep(NA, length(sample_list_ZG66_PB))
for (i in 1:length(sample_list_ZG66_PB)){
  sample_index_ZG66_PB[i] <- which(metadata_ZG66$SAMPLENAME == sample_list_ZG66_PB[i])
}
```
#TBI MONKEY SAMPLE LISTS --> only Gr 
```{r}
df_counts_ZK22<- df_counts_ZK22[,metadata_ZK22$SAMPLENAME]

# Make sure everything is numeric
df_counts_ZK22<- data.frame(apply(df_counts_ZK22, 2,            
                                  function(x) as.numeric(as.character(x))),
                            row.names = rownames(df_counts_ZK22))

sample_list_ZK22_PB <- read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/samplelist/PB/ZK22_PB_Gr_samplelist.txt",sep = "\t", header=F)

colnames(sample_list_ZK22_PB) <- "SAMPLENAME"
sample_list_ZK22_PB<-sample_list_ZK22_PB$SAMPLENAME

# find the indices corresponding to each sample in the metadata & countdata  
sample_index_ZK22_PB <- rep(NA, length(sample_list_ZK22_PB))
for (i in 1:length(sample_list_ZK22_PB)){
  sample_index_ZK22_PB[i] <- which(metadata_ZK22$SAMPLENAME == sample_list_ZK22_PB[i])
}
```

```{r}
df_counts_ZH19<- df_counts_ZH19[,metadata_ZH19$SAMPLENAME]

# Make sure everything is numeric
df_counts_ZH19<- data.frame(apply(df_counts_ZH19, 2,            
                                  function(x) as.numeric(as.character(x))),
                            row.names = rownames(df_counts_ZH19))

sample_list_ZH19_PB <- read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/samplelist/PB/ZH19_PB_Gr_samplelist.txt",sep = "\t", header=F)

colnames(sample_list_ZH19_PB) <- "SAMPLENAME"
sample_list_ZH19_PB<-sample_list_ZH19_PB$SAMPLENAME

# find the indices corresponding to each sample in the metadata & countdata  
sample_index_ZH19_PB <- rep(NA, length(sample_list_ZH19_PB))
for (i in 1:length(sample_list_ZH19_PB)){
  sample_index_ZH19_PB[i] <- which(metadata_ZH19$SAMPLENAME == sample_list_ZH19_PB[i])
}
```

```{r}
df_counts_ZH33<- df_counts_ZH33[,metadata_ZH33$SAMPLENAME]

# Make sure everything is numeric
df_counts_ZH33<- data.frame(apply(df_counts_ZH33, 2,            
                                  function(x) as.numeric(as.character(x))),
                            row.names = rownames(df_counts_ZH33))

sample_list_ZH33_PB <- read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/samplelist/PB/ZH33_PB_Gr_samplelist.txt",sep = "\t", header=F)

colnames(sample_list_ZH33_PB) <- "SAMPLENAME"
sample_list_ZH33_PB<-sample_list_ZH33_PB$SAMPLENAME

# find the indices corresponding to each sample in the metadata & countdata  
sample_index_ZH33_PB <- rep(NA, length(sample_list_ZH33_PB))
for (i in 1:length(sample_list_ZH33_PB)){
  sample_index_ZH33_PB[i] <- which(metadata_ZH33$SAMPLENAME == sample_list_ZH33_PB[i])
}
```
```{r}
df_counts_ZJ31<- df_counts_ZJ31[,metadata_ZJ31$SAMPLENAME]

# Make sure everything is numeric
df_counts_ZJ31<- data.frame(apply(df_counts_ZJ31, 2,            
                                  function(x) as.numeric(as.character(x))),
                            row.names = rownames(df_counts_ZJ31))

sample_list_ZJ31_PB <- read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/samplelist/PB/ZJ31_PB_Gr_samplelist.txt",sep = "\t", header=F)

colnames(sample_list_ZJ31_PB) <- "SAMPLENAME"
sample_list_ZJ31_PB<-sample_list_ZJ31_PB$SAMPLENAME

# find the indices corresponding to each sample in the metadata & countdata  
sample_index_ZJ31_PB <- rep(NA, length(sample_list_ZJ31_PB))
for (i in 1:length(sample_list_ZJ31_PB)){
  sample_index_ZJ31_PB[i] <- which(metadata_ZJ31$SAMPLENAME == sample_list_ZJ31_PB[i])
}
```

```{r}
sample_list_ZG66_PB_Gr <- read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/samplelist/PB/ZG66_PB_Gr_samplelist.txt",sep = "\t", header=F)

colnames(sample_list_ZG66_PB_Gr) <- "SAMPLENAME"
sample_list_ZG66_PB_Gr<-sample_list_ZG66_PB_Gr$SAMPLENAME

# find the indices corresponding to each sample in the metadata & countdata  
sample_index_ZG66_PB_Gr <- rep(NA, length(sample_list_ZG66_PB_Gr))
for (i in 1:length(sample_list_ZG66_PB_Gr)){
  sample_index_ZG66_PB_Gr[i] <- which(metadata_ZG66$SAMPLENAME == sample_list_ZG66_PB_Gr[i])
}
```



###########Figure 2A###########
#select peripheral blood samples from each animal's SE
```{r}
first_PB_sample_selection<- colData(first_SE)$SAMPLENAME[sample_index_first_PB]
second_PB_sample_selection<- colData(second_SE)$SAMPLENAME[sample_index_second_PB]
third_PB_sample_selection <- colData(third_SE)$SAMPLENAME[sample_index_third_PB]
ZG66_PB_sample_selection<-colData(ZG66_SE)$SAMPLENAME[sample_index_ZG66_PB]
ZJ31_PB_sample_selection<-colData(ZJ31_SE)$SAMPLENAME[sample_index_ZJ31_PB]
ZH33_PB_sample_selection<-colData(ZH33_SE)$SAMPLENAME[sample_index_ZH33_PB]
ZK22_PB_sample_selection<-colData(ZK22_SE)$SAMPLENAME[sample_index_ZK22_PB]
ZH19_PB_sample_selection<-colData(ZH19_SE)$SAMPLENAME[sample_index_ZH19_PB]

```

#input the PB samplenames to help generate nice-looking heatmaps that are easy to read without further annotation
```{r}
first_PB_samplenames<- paste(paste(metadata_df_first[sample_index_first_PB, ]$Month_timepoint, "m", sep = "_"), metadata_df_first[sample_index_first_PB, ]$Other, metadata_df_first[sample_index_first_PB, ]$Cell.Type)

second_PB_samplenames<-paste(paste(metadata_df_second[sample_index_second_PB, ]$Month_timepoint, "m", sep = "_"), paste(metadata_df_second[sample_index_second_PB, ]$Experiment, metadata_df_second[sample_index_second_PB, ]$Other, sep="_"), metadata_df_second[sample_index_second_PB, ]$Cell.Type)

third_PB_samplenames<-paste(paste(metadata_df_third[sample_index_third_PB, ]$Month_timepoint, "m", sep = "_"), paste(metadata_df_third[sample_index_third_PB, ]$Experiment, metadata_df_third[sample_index_third_PB, ]$Other, sep="_"), metadata_df_third[sample_index_third_PB, ]$Cell.Type)
#treat 3m GR as 4m Gr

ZG66_PB_sample_names<-paste(paste(metadata_ZG66[sample_index_ZG66_PB, ]$Month_timepoint, "m", sep = "_"), metadata_ZG66[sample_index_ZG66_PB, ]$Other, metadata_ZG66[sample_index_ZG66_PB, ]$simple_cell_type)
```

#generate the PB heatmaps
```{r}
first_PB_heatmap<-barcode_ggheatmap_first(first_SE[,first_PB_sample_selection],
                                            plot_labels = first_PB_samplenames,  
                                            n_clones = 10, label_size = 6, cellnote_size = 3, your_title = "11021142 PB Heatmap")
second_PB_heatmap<-barcode_ggheatmap(second_SE[,second_PB_sample_selection], plot_labels = second_PB_samplenames,
                                     n_clones = 10,label_size = 6, cellnote_size = 3, your_title = "10U004 PB Heatmap")
third_PB_heatmap<-barcode_ggheatmap(third_SE[,third_PB_sample_selection], plot_labels = third_PB_samplenames, n_clones = 10, label_size = 6, cellnote_size = 3, your_title = "H84D PB Heatmap")
ZG66_PB_heatmap<-barcode_ggheatmap(ZG66_SE[,ZG66_PB_sample_selection],
                                   plot_labels = ZG66_PB_sample_names, 
                                   n_clones = 10, label_size = 6, cellnote_size = 3, your_title = "ZG66 PB Heatmap")

```
#read out PB heatmaps
```{r}
first_PB_heatmap
second_PB_heatmap
third_PB_heatmap
ZG66_PB_heatmap
```
###########Figure 2C-E###########



#generate unique clonal counts

```{r}
first_clonal_counts_unique<-clonal_count_v3(first_SE[,first_PB_sample_selection], plot_over = "Month_timepoint", 
                                                   group_by = "Cell.Type", group_by_choices = c("T", "B","Mono", "Gr","CD16+" ,"CD56+"), line_size = 1, 
                                                   cumulative = F, your_title = "11021142 Unique Clonal Count")

second_clonal_count_unique<-clonal_count_v3(second_SE[,second_PB_sample_selection], 
                                                 plot_over = "Month_timepoint", group_by = "Cell.Type", 
                                                 group_by_choices =c("T", "B","Mono", "Gr","CD16+" ,"CD56+"),  
                                                 line_size = 1, cumulative = F, your_title = "10U004 Unique Clonal Count")

third_clonal_counts_unique<-clonal_count_v3(third_SE[,third_PB_sample_selection], plot_over = "Month_timepoint",
                                             group_by = "Cell.Type", group_by_choices = c("T", "B","Mono", "Gr","CD16+" ,"CD56+"), 
                                             cumulative = F, line_size = 1, your_title = "H84D Unique Clonal Count")

```
```{r}
first_clonal_counts_unique
second_clonal_count_unique
third_clonal_counts_unique
```
```{r}
first_clonal_counts_cumulative<-clonal_count_v3(first_SE[,first_PB_sample_selection], plot_over = "Month_timepoint", 
                                                   group_by = "Cell.Type", group_by_choices = c("T", "B","Mono", "Gr","CD16+" ,"CD56+"), line_size = 1, 
                                                   cumulative = T, plot_total_cum = T, your_title = "11021142 Cumulative Clonal Count")

second_clonal_count_cumulative<-clonal_count_v3(second_SE[,second_PB_sample_selection], 
                                                 plot_over = "Month_timepoint", group_by = "Cell.Type", 
                                                 group_by_choices =c("T", "B","Mono", "Gr","CD16+" ,"CD56+"),  
                                                 line_size = 1,  cumulative = T, plot_total_cum = T,your_title = "10U004 Cumulative Clonal Count")

third_clonal_counts_cumulative<-clonal_count_v3(third_SE[,third_PB_sample_selection], plot_over = "Month_timepoint",
                                             group_by = "Cell.Type", group_by_choices = c("T", "B","Mono", "Gr","CD16+" ,"CD56+"), 
                                             cumulative = T, plot_total_cum = T, line_size = 1, your_title = "H84D Cumulative Clonal Count")

```
```{r}
first_clonal_counts_cumulative
second_clonal_count_cumulative
third_clonal_counts_cumulative
```

```{r}
first_shannon_diversity<-clonal_diversity(first_SE[,first_PB_sample_selection],
  plot_over= "Month_timepoint",
  keep_numeric = TRUE,
  group_by = "Cell.Type",
  group_by_choices = c("T", "B", "Mono", "Gr", "CD16+", "CD56+"),
    plot_over_display_choices = c("1",
                            "3","6.5","12", "18.5","24","30","36"),
  index_type = "shannon",
  point_size = 3,
  line_size = 1,
  text_size = 12,
  your_title = NULL)

second_shannon_diversity<-clonal_diversity(
  second_SE[,second_PB_sample_selection],
  plot_over= "Month_timepoint",
  plot_over_display_choices = c("1.5",
                               "2","3","5","9", "16","22.5"),
  keep_numeric = TRUE,
  group_by = "Cell.Type",
  group_by_choices = c("T", "B", "Mono", "Gr","CD16+"
                       ,"CD56+"),
  index_type = "shannon",
  point_size = 3,
  line_size = 1,
  text_size = 12,
  your_title = "10U004 Shannon Diversity Plot",
  return_table = FALSE)

third_shannon_diversity<-clonal_diversity(
  third_SE[,third_PB_sample_selection],
  plot_over= "Month_timepoint",
  keep_numeric = TRUE,
  group_by = "Cell.Type",
  group_by_choices = c("T", "B", "Mono", "Gr", "CD16+", "CD56+"),
  index_type = "shannon",
  point_size = 3,
  line_size = 1,
  text_size = 12,
  your_title = "H84D Shannon Diversity Plot",
  return_table = FALSE)


```
```{r}
first_shannon_diversity
second_shannon_diversity
third_shannon_diversity
```

#clonal counts Gr tables
```{r}
ZG66_clonal_counts_cumulative_table<-clonal_count_v3(ZG66_SE[,ZG66_PB_sample_selection], plot_over = "Month_timepoint",
                                                 group_by = "simple_cell_type", group_by_choices ="Gr",
                                                 line_size = 1, cumulative = T, plot_total_cum = T, 
                                                 your_title = "ZG66 PB Gr Cumulative Clonal Count", return_table = T) 
ZJ31_clonal_counts_cumulative_table<-clonal_count_v3(ZJ31_SE[,ZJ31_PB_sample_selection], plot_over = "months",
                                                 group_by = "simple_cell_type", group_by_choices = "Gr",
                                                 line_size = 1, cumulative = T, plot_total_cum = T, your_title = "ZJ31 Cumulative PB Gr Clonal Count", return_table = T) 
ZH33_clonal_counts_cumulative_table<-clonal_count_v3(ZH33_SE[,ZH33_PB_sample_selection], plot_over = "Month_timepoint",
                                                 group_by = "simple_cell_type", group_by_choices = "Gr",
                                                 line_size = 1, cumulative = T, plot_total_cum = T, your_title = "ZH33 PB Gr Cumulative PB Gr Clonal Count", return_table = T) 

ZH19_clonal_counts_cumulative_table<-clonal_count_v3(ZH19_SE[,ZH19_PB_sample_selection], plot_over = "Month_timepoint",
                                                 group_by = "simple_cell_type", group_by_choices = "Gr",
                                                 line_size = 1, cumulative = T, plot_total_cum = T, your_title = "ZH19 PB Gr Cumulative PB Gr Clonal Count", return_table = T)

ZK22_clonal_counts_cumulative_table<-clonal_count_v3(ZK22_SE[,ZK22_PB_sample_selection], plot_over = "Month_timepoint",
                                                 group_by = "simple_cell_type", group_by_choices = "Gr",
                                                 line_size = 1, cumulative = T, plot_total_cum = T, your_title = "ZH19 PB Gr Cumulative PB Gr Clonal Count", return_table = T)
```

```{r}
ZG66_clonal_counts_unique_table<-clonal_count_v3(ZG66_SE[,ZG66_PB_sample_selection], plot_over = "Month_timepoint",
                                                 group_by = "simple_cell_type", group_by_choices ="Gr",
                                                 line_size = 1, cumulative = F,  
                                                 your_title = "ZG66 PB Gr Unique Clonal Count", return_table = T) 
ZJ31_clonal_counts_unique_table<-clonal_count_v3(ZJ31_SE[,ZJ31_PB_sample_selection], plot_over = "months",
                                                 group_by = "simple_cell_type", group_by_choices = "Gr",
                                                 line_size = 1, cumulative = F,  your_title = "ZJ31 Unique PB Gr Clonal Count", return_table = T) 
ZH33_clonal_counts_unique_table<-clonal_count_v3(ZH33_SE[,ZH33_PB_sample_selection], plot_over = "Month_timepoint",
                                                 group_by = "simple_cell_type", group_by_choices = "Gr",
                                                 line_size = 1, cumulative = F, your_title = "ZH33 Unique PB Gr Clonal Count", return_table = T) 

ZH19_clonal_counts_unique_table<-clonal_count_v3(ZH19_SE[,ZH19_PB_sample_selection], plot_over = "Month_timepoint",
                                                 group_by = "simple_cell_type", group_by_choices = "Gr",
                                                 line_size = 1, cumulative = F,  your_title = "ZH19 Unique PB Gr Clonal Count", return_table = T)

ZK22_clonal_counts_unique_table<-clonal_count_v3(ZK22_SE[,ZK22_PB_sample_selection], plot_over = "Month_timepoint",
                                                 group_by = "simple_cell_type", group_by_choices = "Gr",
                                                 line_size = 1, cumulative = F, your_title = "ZH19 Unique PB Gr Clonal Count", return_table = T)
```

```{r}
ZG66_shannon_table<-clonal_diversity(ZG66_SE[,ZG66_PB_sample_selection], plot_over = "Month_timepoint",
                                                 group_by = "simple_cell_type", group_by_choices ="Gr",
                                                 line_size = 1, 
                                                 your_title = "ZG66 Shannon Diversity", return_table = T) 
ZH19_shannon_table<-clonal_diversity(ZH19_SE_shannon[,ZH19_PB_sample_selection], plot_over = "Month_timepoint",
                                                 group_by = "simple_cell_type", group_by_choices ="Gr",
                                                 line_size = 1, 
                                                 your_title = "ZH19 Shannon Diversity", return_table = T) 
ZH33_shannon_table<-clonal_diversity(ZH33_SE_shannon[,ZH33_PB_sample_selection], plot_over = "Month_timepoint",
                                                 group_by = "simple_cell_type", group_by_choices ="Gr",
                                                 line_size = 1, 
                                                 your_title = "ZH33 Shannon Diversity", return_table = T) 
ZJ31_shannon_table<-clonal_diversity(ZJ31_SE_shannon[,ZJ31_PB_sample_selection], plot_over = "months",
                                                 group_by = "simple_cell_type", group_by_choices ="Gr",
                                                 line_size = 1, 
                                                 your_title = "ZJ31 Shannon Diversity", return_table = T) 
ZK22_shannon_table<-clonal_diversity(ZK22_SE_shannon[,ZK22_PB_sample_selection], plot_over = "Month_timepoint",
                                                 group_by = "simple_cell_type", group_by_choices ="Gr",
                                                 line_size = 1, 
                                                 your_title = "ZK22 Shannon Diversity", return_table = T) 
```


#generate cumulative clonal count tables for busulfan monkeys
```{r}
first_clonal_counts_cumulative_table<-clonal_count_v3(first_SE[,first_PB_sample_selection], plot_over = "Month_timepoint", 
                                                   group_by = "Cell.Type", group_by_choices = c("T", "B","Mono", "Gr","CD16+" ,"CD56+"), line_size = 1, 
                                                   cumulative = T, plot_total_cum = T, your_title = "11021142 Cumulative Clonal Count", return_table = T)

second_clonal_counts_cumulative_table<-clonal_count_v3(second_SE[,second_PB_sample_selection], 
                                                 plot_over = "Month_timepoint", group_by = "Cell.Type", 
                                                 group_by_choices =c("T", "B","Mono", "Gr","CD16+" ,"CD56+"),  
                                                 line_size = 1, cumulative = T, plot_total_cum = T, your_title = "10U004 Cumulative Clonal Count", return_table = T)

third_clonal_counts_cumulative_table<-clonal_count_v3(third_SE[,third_PB_sample_selection], plot_over = "Month_timepoint",
                                             group_by = "Cell.Type", group_by_choices = c("T", "B","Mono", "Gr","CD16+" ,"CD56+"), 
                                             cumulative = T, line_size = 1, plot_total_cum = T, your_title = "H84D Cumulative Clonal Count", return_table = T)

```



