---
title: "Busulfan Manuscript Figure 2B_revised"
author: "Diana M Abraham"
date: '2022-10-04'
output: html_notebook
---

##################SETTING UP###################
#if first time using barcodetrackR
```{r}
install.packages("barcodetrackR")
install.packages("magrittr")
install.packages("SummarizedExperiment")
```

#load up the necessary packages and libraries and functions
```{r}
installed.packages("barcodetrackR")
installed.packages("magrittr")
installed.packages("SummarizedExperiment")
library(dplyr)
library(barcodetrackR)
library (rlang)
library(ggplot2)
library(RColorBrewer)
require("magrittr")
require("barcodetrackR")
require("SummarizedExperiment")
#we adjusted the barcodetrackR package and so here is the customized function that we used to calculate the cumulative counts
clonal_count_v3<-source("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/customized_functions/clonal_counts_v3.R") 
clonal_count_v3<-clonal_count_v3$value

#we adjusted the barcodetrackR package to accomodate for the low clonal contributions from later timepoints in the animal: 11021142 - so we read in a customized barcode ggheatmap function for that animal's analysis 
barcode_ggheatmap_first<-source("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/customized_functions/barcode_ggheatmap_42.R")
barcode_ggheatmap_first<-barcode_ggheatmap_first$value
autocorrelation.plot<-source("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/customized_functions/autocorrelation_plot.R")
autocorrelation.plot<-autocorrelation.plot$value
```
########FIGURE 2B##############
#set up autocorrelation plot

#load data for comparison animals (TBI animals)
```{r}
my_path<-"/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/autocorrelation_data/"

#ZG66
zg66.counts <- read.delim(file.path(my_path,"ZG66/ZG66_combined_20180821.txt"), header=T, row.names=1, sep="\t")
zg66.key=read.delim(file.path(my_path,"ZG66/ZG66_key_20180821.txt"))
zg66_sample_list <- as.vector(unlist(read.delim("/Volumes/dirgroup/TSCBB/LAB/Diana/busulfan_manuscript/autocorrelation_data/ZG66/grans_samplelist.txt",header=F)))
zg66.grans.samples <- as.vector(zg66.key$FILENAME[match(zg66_sample_list,zg66.key$GIVENNAME)])
zg66.time <- NULL
zg66.grans.samples[9]<-"zg66_20150615sample_Grans_ficoll_CD102_R12_CTTGTA_L006_R1_001.fastq"
zg66.time$grans=c(1,2,3,4.5,6.5,12,17,27,30,36)
#ZH19
zh19.counts <- read.delim(file.path(my_path,"ZH19/ZH19_combined_20180823.txt"), header=T, row.names=1, sep="\t")
zh19.key=read.delim(file.path(my_path,"ZH19/ZH19_key_20180823.txt"))
zh19_sample_list <- as.vector(unlist(read.delim(file.path(my_path,"ZH19/grans_samplelist.txt"),header=F)))
zh19.grans.samples <- as.vector(zh19.key$FILENAME[match(zh19_sample_list,zh19.key$GIVENNAME)])
zh19.time <- NULL
zh19.grans.samples[10]<-"pp_50trim_ZH19_41m_20161013_PB_Grans_cell_DNA_R5_FX17.fastq"
zh19.grans.samples[9]<-"pp_50trim_zh19_28m_Gr_DiegoDemultiplex.fastq"
zh19.grans.samples[8]<-"zh1915hmGFPpCD33predoCD96R26.fastq"
zh19.time$grans=c(1,2,3,6,7,12,15.5,22,28,41)
#ZH33
zh33.counts <- read.delim(file.path(my_path,"ZH33/ZH33_combined_20180806.txt"), header=T, row.names=1, sep="\t")
zh33.key=read.delim(file.path(my_path,"ZH33/ZH33_key_20180806.txt"))
zh33_sample_list <- as.vector(unlist(read.delim(file.path(my_path,"ZH33/grans_samplelist.txt"),header=F)))
zh33.grans.samples <- as.vector(zh33.key$FILENAME[match(zh33_sample_list,zh33.key$GIVENNAME)])
zh33.grans.samples[11]<-"zh33_20150806_PB_Gr_Ficoll_CD_104_R12_CTTGTA_L005_R1_001.fastq"
zh33.time <- NULL
zh33.time$grans=c(1,2,3,4.5,6.5,12,14,21,23,28,38)
#ZJ31
zj31.counts <- read.delim(file.path(my_path,"ZJ31/ZJ31_combined_20180806.txt"), header=T, row.names=1, sep="\t")
zj31.grans.samples=as.vector(unlist(read.delim(file.path(my_path,"ZJ31/grans_samplelist.txt"),header=F)))
zj31.time <- NULL
zj31.time$grans=c(1,2,3,4,6,8.5,9.5,12,17.5,20,28,35.5)

#ZK22
zk22.counts <- read.delim(file.path(my_path,"ZK22/ZK22_combined_20190326.txt"), header=T, row.names=1, sep="\t")
zk22.key=read.delim(file.path(my_path,"ZK22/ZK22_key_20190326.txt"))
zk22_sample_list <- as.vector(unlist(read.delim(file.path(my_path,"ZK22/grans_samplelist.txt"),header=F))) # ignore the warning
zk22.grans.samples <- as.vector(zk22.key$FILENAME[match(zk22_sample_list,zk22.key$GIVENNAME)])
zk22.time <- NULL
zk22.time$grans=c(2,3.5,5,7,9,15.5,27,37) #no 1 month in these files
```

#load data for busulfan animals

```{r}
#11021142
M11021142.counts <- read.delim(file.path(my_path,"11021142/M11021142_combined_20220510_lib15_corrected.txt"), header=T, row.names=1, sep="\t")
M11021142.key=read.delim(file.path(my_path,"11021142/M11021142_key_20220510.txt"))
M11021142.grans.samples=as.vector(unlist(read.delim(file.path(my_path,"11021142/grans_samplelist_up2_18hm.txt"),header=F)))
M11021142.time <- NULL
M11021142.time$grans=c(1,3,6,9,13)

# 10U004
M10U004.counts <- read.delim(file.path(my_path,"10U004/M10U004_combined_20220509_lib15_corrected.txt"), header=T, row.names=1, sep="\t")
M10U004.key=read.delim(file.path(my_path,"10U004/M10U004_key_20220509.txt"))
M10U004.grans.samples=as.vector(unlist(read.delim(file.path(my_path,"10U004/grans_samplelist.txt"),header=F)))
M10U004.time <- NULL
M10U004.time$grans=c(1.5,2,3,5,9,16,20,22.5,26)

# H84D
H84D.counts <- read.delim(file.path(my_path,"H84D/H84D_combined_20220510_lib21_corrected.txt"), header=T, row.names=1, sep="\t")
H84D.key=read.delim(file.path(my_path,"H84D/H84D_key_20220510.txt"))
H84D.grans.samples=as.vector(unlist(read.delim(file.path(my_path,"H84D/grans_samplelist.txt"),header=F)))
H84D.time <- NULL
H84D.time$grans=c(1,2,3,6,9,12,14.5,18)
```


```{r}
auto_plot<-(autocorrelation.plot(list(M11021142.counts[,M11021142.grans.samples],
                          M10U004.counts[,M10U004.grans.samples],
                          H84D.counts[,H84D.grans.samples],
                          zg66.counts[,zg66.grans.samples],
                          zh19.counts[,zh19.grans.samples],
                          zh33.counts[,zh33.grans.samples],
                          zj31.counts[,zj31.grans.samples],
                          zk22.counts[,zk22.grans.samples]),
                     list(M11021142.time$grans,
                          M10U004.time$grans,
                          H84D.time$grans,
                          zg66.time$grans,
                          zh19.time$grans,
                          zh33.time$grans,
                          zj31.time$grans,
                          zk22.time$grans),
                     Monkey=c("11021142","10U004","H84D","ZG66","ZH19","ZH33","ZJ31","ZK22")))